---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# youRtube

<!-- badges: start -->
<!-- badges: end -->

The goal of youRtube is to easily gather data and create visualizations from YouTube API data. 

## Installation

You can install the the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rnevils/youRtube")
```

```{r}
library(youRtube)
```

## Getting Started

To use this package you need a YouTube API key. See [here](https://developers.google.com/youtube/v3/getting-started) for how to get a key.

Save your API key as a string called "key" for easy use with the functions in the package

```{r, eval = F}
key <- "AIzaSyBAbuMv8NG47mox9ebPv9QWsuY9j3k2Ojd"
```
```{r, echo = F }
key <- "AIzaSyBAbuMv8NG47mox9ebPv9QWNOxvzmQwGxs"
```

## Most Popular Videos Data

Use the function `get_top_videos` to create a data frame of the current top trending videos on YouTube. You can specify which region and content category you are interested in.

Overall top trending videos in the US
```{r, eval = F}
top50_us <- get_top_videos(key, n = 50)
```
Top trending music videos in Great Britian
```{r, eval = F}
top10_uk_music <- get_top_videos(key, region = "United Kingdom", category = "Music")
```

Use `get_region_list()` and `get_category_list()` to see YouTube's regions and content categories.

```{r}
head(get_region_list(key))
head(get_category_list(key, region = "Sweden"))
```

Use the function `graph_top_videos_category()` to see the overall top trending videos broken down by content category.

```{r, message = F}
graph_top_videos_category(key, n = 25)
graph_top_videos_category(key, region = "United Kingdom", n = 25)
```

The `comment_cloud` function also needs a Youtube video ID. To find the Id of a youtube video look at the url and find the last part after the **v=**

For example in `https://www.youtube.com/watch?v=QjA5faZF1A8` the Id would be `QjA5faZF1A8`


